\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-04-23 trunk/arch.tex
updates to reviews

Traditionally planning has been deemed computationally expensive with
planner performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash if
the internal state of the plan gets out of synch with the actual state
of the world. As a result the planning problem managed {\em in situ}
has traditionally remained fairly detached from low-level
control. Most adaptations at the lower-level reactive layers in
contrast are managed by specialized components (for example
\texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with a unified declarative model. Our approach with \rx
builds on this design methodology albeit in a substantially systematic
manner. The \rx architecture contributes to agent architectures over
and beyond \texttt{IDEA} are in the following ways:

@@

\item \emph{Partitioning} the global planning problem into multiple
  decision loops, called {\em reactors}. Each reactor has its own
  scope both functionally (one for example focusing on the conversion
  of high level waypoints into low-level commands) and temporally as
  each reactor declares its planning look-ahead $\pi$ and expected
  latency $\lambda$ before being able to produce plan to the agent
  depending on where it is located in a reactor dependency graph such
  as shown in Fig. \ref{fig:agent}. A reactor closer to the hardware
  in the hierarchy, is expected to deliberate less and be highly
  responsive to observations from the world. This implies lower values
  of $\pi$ and $\lambda$ (see Section \ref{sec:arch:trex} below).

\item \emph{Coupling} a tighter integration between the planning
  process and world evolution to ensure that planning occurs
  \emph{during continuous} state update in the {\em same} polan
  database used for planning. By doing so, the planner is
  better informed in its deliberation despite a larger latency than
  the changing world. 
\end{itemize}

@@

\begin{figure}[b]
  \centering
  \subfloat[\small When the \texttt{Sampling} reactor fails to
  synchronize, it is removed from the reactor dependency graph along
  with all its {\em internal} timelines while generating a \texttt{Failed} observation]{\includegraphics[width=0.35\columnwidth]{figs/AUV-fail0.pdf}
  \label{fig:fail0}}
  \qquad
  \subfloat[\small In the worst case this \texttt{Failed} observation may imply
  other reactors that depend on the \texttt{Sampling} reactor might fail to
  synchronize leading to a bottom-up destruction of ``faulty'' reactors.]{
    \includegraphics[width=0.35\columnwidth]{figs/AUV-fail1}\label{fig:fail1}}
  \caption{\small Impact of the \texttt{Sampling} reactor failure in
    the AUV agent shown in Fig. \ref{fig:agent}}
\end{figure}

@@

Steps $2$ \& $3$ above are handled by the \eu solver from algorithm
\ref{alg:europa:solve} which ensures that the {\em current state
  flaws} are selected last so as to follow the sequence given
above.

>>>>

Traditionally planning has been deemed computationally expensive with
planner performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash if
the internal state of the plan gets out of synch with the actual state
of the world. As a result the planning problem managed {\em in situ}
has traditionally remained fairly detached from low-level
control. Most adaptations at the lower-level reactive layers in
contrast are managed by specialized components (for example
\texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with \kcomment{an} unified declarative model. Our approach
with \rx builds on this design methodology albeit in a substantially
systematic manner. The \rx architecture contributes to agent
architectures over and beyond \texttt{IDEA} in the following
\kcomment{significant} ways:

@@

\item \emph{Partitioning} the global planning problem into multiple
  decision loops, called {\em reactors}. Each reactor has its own
  scope both functionally (one for example focusing on the conversion
  of high level waypoints into low-level commands) and temporally as
  each reactor declares its planning look-ahead $\pi$ and expected
  latency $\lambda$ before being able to produce \kcomment{a} plan to
  the agent depending on where it is located in a reactor dependency
  graph such as shown in Fig. \ref{fig:agent}. A reactor closer to the
  hardware in the hierarchy, is expected to deliberate less and be
  highly responsive to observations from the world. This implies lower
  values of $\pi$ and $\lambda$ (see Section \ref{sec:arch:trex}
  below).

\item \emph{Coupling} a tighter integration between the planning
  process and world evolution to ensure that planning occurs
  \emph{during continuous} state update in the {\em same}
  \kcomment{plan} database used for planning. By doing so, the planner
  is better informed in its deliberation despite a larger latency than
  the changing world.
\end{itemize}

@@

\begin{figure}[b]
  \centering
  \subfloat[\small When the \texttt{Sampling} reactor fails to
  synchronize, it is removed from the reactor dependency graph along
  with all its {\em internal} timelines while generating a \texttt{Failed} observation]{\includegraphics[width=0.35\columnwidth]{figs/AUV-fail0.pdf}
  \label{fig:fail0}}
  \qquad
  \subfloat[\small In the worst case this \texttt{Failed} observation may imply
  other reactors that depend on the \texttt{Sampling} reactor might fail to
  synchronize leading to a bottom-up destruction of ``faulty'' reactors.]{
    \includegraphics[width=0.35\columnwidth]{figs/AUV-fail1}\label{fig:fail1}}
  \caption{\small Impact of the \texttt{Sampling} reactor failure in
    the AUV agent \kcomment{from} Fig. \ref{fig:agent}}
\end{figure}

@@

Steps $2$ \& $3$ above are handled by the \eu solver from Algorithm
\ref{alg:europa:solve} which ensures that the {\em current state
  flaws} are selected last so as to follow the sequence given above.

### 2012-04-23 trunk/europa-basics.tex
updates to reviews

\rx is an adaptive, artificial intelligence based controller and
provides general framework for building reasoning systems for
real-world autonomous vehicles. At MBARI \rx is used for AUV control;
another instantiation of the system is being used for control of a
terrestrial personal robot \cite{pr2, Meeussen:2010dn}. The
development of \rx has been targeted at surveying a number of
oceanographic features which are dynamic and spatio-temporally
unpredictable. Typically this requires our AUVs to balance the goals
of coverage spatially while opportunistically following features of
scientific interest and to do so while being aware of its own
limitations in terms of resources (\eg the battery state of charge)
and overall proximity to other observational assets for obtaining
scientific ground-truth. We are interested in representational
frameworks that allow robots to pursue long-term objectives while
choosing short-term gain and can gracefully deal with exogenous or
endogenous change.

@@

Planning as an activity is ingrained in human decision-making
\cite{berthoz} and its generalization into a computational framework
demonstrating machine intelligence long targeted by pioneers in
computer science \cite{computersthought}. Early work in this context
focused on logical theorem proving by computer \cite{green69} which
has formed the basis of much of the discipline of AI Planning. The
emphasis in these early attempts was to logically derive the existence
proof of a trajectory of actions for a hypothetical robot (moving
blocks, chess pieces, furniture etc) to achieve a specific goal given
specific initial conditions. Two important properties of
\emph{Soundness}\footnote{A planning algorithm is sound if invoked on
  a problem $P$ returns a plan which is a solution for $P$.} and
\emph{Completeness}\footnote{A planning algorithm is complete if
  invoked on a solvable problem $P$ is guaranteed to return a
  solution.} along with derived results for algorithmic complexity
\cite{corman} were a defining cornerstone for understanding how
different computational paradigms could actually be tractable first in
simulation and subsequently in actual robotic platforms. In this
chapter our emphasis is to focus on embedded AI Planning and the
execution of plans on an embedded robotic marine robotic
platform. While the platform is domain specific, the techniques we
highlight are general purpose as noted in Section \ref{sec:intro}.

@@

\begin{figure}[t]
\centering
\subfloat[\small A \eu solution to an \texttt{RCPSP} \cite{Bruckera99}
  problem.]{\label{fig:rcpsp-1}\includegraphics[scale=0.2]{figs/Example-UBO0.jpg}}\qquad
\subfloat[\small A \eu solution to a shopping agent problem domain where
  the agent needs to buy Bananas, Milk and a Drill.]{\label{fig:shopping-1}\includegraphics[scale=0.25]{figs/Example-Shopping0.jpg}}
\caption{\small \eu based solutions to scheduling and planning problems.}
\end{figure}

@@

To generate plans, the \texttt{CAIP} framework uses a plan-space search
approach \cite{ghallab04}, where a partial plan is evolved until all
open goals are achieved, and all inconsistencies are removed. The
specific search algorithm used by \eu will be covered in detail below.

>>>>

\rx is an adaptive, artificial intelligence based controller and
provides \kcomment{a} general framework for building reasoning systems
for real-world autonomous vehicles. At MBARI \rx is used for AUV
control; another instantiation of the system is being used for control
of a terrestrial personal robot \cite{pr2, Meeussen:2010dn}. The
development of \rx has been targeted at surveying a number of
oceanographic features which are dynamic and spatio-temporally
unpredictable. Typically this requires our AUVs to balance the goals
of coverage spatially while opportunistically following features of
scientific interest and to do so while being aware of its own
limitations in terms of resources (\eg the battery state of charge)
and overall proximity to other observational assets for obtaining
scientific ground-truth. We are interested in representational
frameworks that allow robots to pursue long-term objectives while
choosing short-term gain and can gracefully deal with exogenous or
endogenous change.

@@

Planning as an activity is ingrained in human decision-making
\cite{berthoz} and its generalization into a computational framework
demonstrating machine intelligence long targeted by pioneers in
computer science \cite{computersthought}. Early work in this context
focused on logical theorem proving by computer \cite{green69} which
has formed the basis of much of the discipline of AI Planning. The
emphasis in these early attempts was to logically derive the existence
proof of a trajectory of actions for a hypothetical robot (moving
blocks, chess pieces, furniture etc) to achieve a specific goal given
specific initial conditions. Two important properties of
\emph{Soundness}\footnote{A planning algorithm is sound if invoked on
  a problem $P$ returns a plan which is a solution for $P$.} and
\emph{Completeness}\footnote{A planning algorithm is complete if
  invoked on a solvable problem $P$ is guaranteed to return a
  solution.} along with derived results for algorithmic complexity
\cite{corman} were a defining cornerstone for understanding how
different computational paradigms could actually be tractable first in
simulation and subsequently in actual robotic platforms. In this
chapter our emphasis is to focus on embedded AI Planning and the
execution of plans on an embedded \kcomment{marine robotic}
platform. While the platform is domain specific, the techniques we
highlight are general purpose as noted in Section \ref{sec:intro}.

@@

\begin{figure}[t]
\centering
\subfloat[\small A \eu solution to an \texttt{RCPSP} \cite{Bruckera99}
  problem.]{\label{fig:rcpsp-1}\includegraphics[scale=0.25]{figs/Example-UBO0.jpg}}\qquad
\subfloat[\small A \eu solution to a shopping agent problem domain where
  the agent needs to buy Bananas, Milk and a Drill.]{\label{fig:shopping-1}\includegraphics[scale=0.3]{figs/Example-Shopping0.jpg}}
\caption{\small \eu based solutions to scheduling and planning problems.}
\end{figure}

@@

To generate plans, the \texttt{CAIP} framework uses a plan-space
search approach \cite{ghallab04}, where a \emph{partial plan} is
evolved until all open goals are achieved and all inconsistencies are
removed. \kcomment{A partial plan is a subsequence of a plan which can
  be refined into a plan structure.} The specific search algorithm
used by \eu will be covered in \kcomment{further} detail below.

### 2012-04-23 trunk/intro.tex
updates to reviews

In this chapter, we propose an alternative view to decision-making
using in-situ automated Planning \cite{ghallab04} and more important
demonstrate that while earlier control paradigms primarily driven by
\emph{reactive} approaches to control can be augmented to not only
provide targeted observation and sampling, but also a more nuanced and
balanced consideration of mission objectives, environmental conditions
and available resources. Planning (or deliberation or projection in
action space) is important to balance current needs of a robot with
future desires or goals. And to do such planning in the context of
time and available resources in-situ on the robot. Planning without
time or action planning in of itself is not adequate; dealing with
time ensures that the balance between now and the future is handled
systematically. Yet, plans have to be tied to robotic action and in
the real-world which is not static. Further, plans project future
state which is not only likely to change, but is based on substantial
uncertainty\footnote{It is important to remember that these principles
  are broad much as Dwight Eisenhower is reputed to have said
  ``\emph{In preparing for battle I have always found that plans are
    useless, but planning is indispensable}'' and ``\emph{Failing to
    plan is planning to fail}''}. Modeling of the marine environment
to provide cues is hampered by poor understanding of the worlds ocean
and poor predictive skill of ocean models and often little to no
availability of a priori synoptic views of the survey area.

AUV control architectures have primarily been driven by reactive
Subsumption-based approaches \cite{brooks86}. They have been adequate
to doing routine straight-line survey tracts which have played a
valuable role in the acceptance of AUVs as a new tool for ocean
science and DoD applications. However, scaling of problem domains in
addition to dealing with event-response and discovery in the
water-column challenges \emph{how} controllers are written in the
first place, maintained and upgraded over the life-cycle of the
platform. Dealing with off-nominal endogenous or exogenous conditions
including sensor failures stretches how AUVs are currently being
utilized; one consequence for instance, is any off-nominal condition
results in a \emph{fail-safe} surface mode to radio for help. Further
these approaches, words to the contrary are not only hard to maintain,
are not 'adaptive' enough. Despite vigorous defense by Brooks early on
\cite{Brooks91intelligencewithoutrea,Brooks91intelligencewithoutrep},
autonomous systems require a model if not of the world then of the 
\emph{physics} of the vehicle when it interacts with the world.

Persistent and early legitimate criticism of deliberation on the other
hand also well articulated by Brooks
\cite{Brooks91intelligencewithoutrea,Brooks91intelligencewithoutrep}
was targeting the performance of in-situ deliberation. Terrestrial
robotic platforms were well-known to frequently stop and ``plan''; 
assuming in the meantime that the world will remain static. In
the marine robotics world, such a situation would simply not be
permissible given the need to make continuous observations without
stopping an under-articulated robotic platform such as an AUV. However
algorithmic and implementational advances by the AI community over the
years has produced a range of planners with demonstrated embedded
capabilities
\cite{simmons94,Haigh98,alami:1998p820,chien00,mus98,teichteil07}. Our
work has been influenced by and in turn influenced a wide range of
activities in the field of AI Planning and Plan Execution with
demonstrated real-world and highly visible capabilities in the Space
domain \cite{mus98,rajan00,aichang04,bresina05} for NASA. Lessons
learned have been applied to the world of marine robotics which we
bring together in this chapter. Important lessons that were derived
from this rich legacy involved the following:

@@

We have developed, tested and deployed the Teleo-Reactive EXecutive
(\texttt{T-REX}) an on-board adaptive control system that integrates
AI based planning and %\sout{probabilistic} 
state estimation in a hybrid executive\cite{mcgann08a,mcgann08b,py10}. 
%  \sout{Probabilistic state estimation integrates a number of science observations to produce a
% likelihood that the vehicle sensors perceive a feature of
% interest}.\fcomment{\rx {\em does not} integrate probabilistic state
%   estimation! ... The HMM estimation was coded on top of \eu model but
%   neither \eu or \rx had explicit management of it} 
State estimation allow the system to keep track of the world evolution
as time advances based on a formal model distributed through the architecture.
Onboard planning and execution enables adaptation of
navigation and instrument control based on the state identified during
state estimation.
% \sout{the probability of having detected such a phenomenon} 
It further enables goal-directed
commanding within the context of projected mission state and allows
for replanning for off-nominal situations and opportunistic science
events. The framework in addition to being used on an AUV, is general
enough be used for controlling a personal robot \cite{mcgann2009} and
is deployed on a European planetary rover testbed
\cite{goac11}. While it is possible to integrate probabilistic
estimation on top of this framework \cite{mcgann08d}, such
representation is not explicitly handled by the framework and is
out of scope of this chapter.
% Probabilistic state estimation through modeling within 
% this framework can be done is discussed elsewhere
% \cite{mcgann08d} and out of scope for this chapter. 
Deliberation and reaction are integrated systematically over different temporal and
functional scopes within a single agent and a single model that covers
the needs of high-level mission management, low-level navigation,
instrument control, and detection of unstructured and poorly
understood phenomena. \rx is deployed on MBARI's Dorado AUV shown in
Fig. \ref{fig:auv-fig}, which to the best of our knowledge is the only
operational marine platform anywhere being used for routine scientific
surveys with onboard plan synthesis.

@@

This chapter is organized as follows. We start with some foundational
concepts in our Planning framework in Section~\ref{sec:concepts} which
includes a brief overview of AI Planning in
Section~\ref{sec:planningfound}. In Section~\ref{sec:basics} we go
deeper into the \eu framework itself, the basis of all deliberation
within \rx. A key portion is Section~\ref{sec:europa:pr} which details
the internal plan representation essential to planning within a
situated agent like \rx. Modeling (Section~\ref{sec:europa:modeling}),
Inference (Section~\ref{sec:europa:inference}) and Search
(Section~\ref{sec:europa:search}) further detail the important details
associated with \eu for the and relevant to how \rx works to the
reader. With these foundational elements out of the way, we transition
to \rx itself, in Section~\ref{sec:arch}, bring out architectural
details in Section~\ref{sec:arch:trex}, deal with the execution cycle
in Section~\ref{sec:arch:exec}, highlight how \rx deliberates in
Section~\ref{sec:arch:europa} finally delving deeper into the key
concept of synchronization in Section~\ref{sec:arch:synch}. Further
details on deliberation within \rx (Section~\ref{sec:arch:plan}) and
how planning and execution are interleaved are shown in
Section~\ref{sec:arch:intertwine}. We offer results from our
experiments at sea in Section~\ref{sec:results}, offer some insights
into the near-term future goals of our research in
Section~\ref{sec:future} and conclude with
Section~\ref{sec:conclusion}.

>>>>

In this chapter, we propose an alternative view to decision-making
using in-situ automated Planning \cite{ghallab04}. More importantly,
we demonstrate that earlier control paradigms (primarily driven by
\emph{reactive} approaches to control) can be augmented to provide
targeted observation and sampling as well as a more nuanced and
balanced consideration of mission objectives, environmental conditions
and available resources. Planning (or deliberation or projection in
action space \kcomment{and used interchangeably in this chapter}) is
important to balance current needs of a robot with future desires or
goals taking into account time and available resources in-situ on the
robot. Planning without time or action planning in and of itself is
not adequate; dealing with time ensures that the balance between now
and the future is handled systematically. Yet, plans have to be tied
to robotic action and in the real-world which is not static. Further,
plans project future state which is not only likely to change, but is
based on substantial uncertainty\footnote{It is important to remember
  that these principles are broad much as Dwight Eisenhower is reputed
  to have said ``\emph{In preparing for battle I have always found
    that plans are useless, but planning is indispensable}'' and
  ``\emph{Failing to plan is planning to fail}''}. Use of
environmental cues is often hampered by poor \kcomment{predictive}
skill \cite{anderson2009} of ocean models and little to no
availability of a priori synoptic views of the survey
area. \kcomment{Planning therefore provides a ``buffer'' against the
  stochastic environment.}

AUV control architectures have primarily been driven by reactive
Subsumption-based approaches \cite{brooks86}. They have been adequate
to doing routine straight-line survey trajectories which have played a
valuable role in the acceptance of AUVs as a new tool for ocean
science and DoD applications. However, scaling of problem domains in
addition to dealing with event-response and discovery in the
water-column challenges \emph{how} controllers are written in the
first place, maintained and upgraded over the life-cycle of the
platform. Dealing with off-nominal endogenous or exogenous conditions
including sensor failures stretches how AUVs are currently being
utilized; one consequence for instance, is any off-nominal condition
results in a \emph{fail-safe} surface mode to radio for help. Software
design using these reactive approaches, not only makes it hard for
sustaining engineering development, these approaches are not
adequately adaptive for emerging ocean science problems.  Despite
vigorous defense by Brooks early on
\cite{Brooks91intelligencewithoutrea,Brooks91intelligencewithoutrep},
autonomous systems require a model if not of the world then of the
\emph{physics} of the vehicle when it interacts with the world.

Criticism of AI planning, on the other hand, also well articulated by
Brooks, was targeting the performance of in-situ
deliberation. Terrestrial robotic platforms were well-known to
frequently stop and ``plan''; assuming in the meantime that the world
will remain static. In the marine robotics world, such a situation
would simply not be permissible given the need to make continuous
observations without stopping an under-articulated robotic platform
such as an AUV. However, algorithmic and implementational advances by
the AI community over the years have produced a range of planners with
demonstrated embedded capabilities
\cite{simmons94,Haigh98,alami:1998p820,chien00,mus98,teichteil07}. Our
work has been influenced by and in turn influenced a wide range of
activities in the field of AI Planning and Plan Execution with
demonstrated real-world and highly visible capabilities in the Space
domain \cite{mus98,rajan00,aichang04,bresina05} for NASA. Lessons
learned have been applied to the world of marine robotics which we
bring together in this chapter. Important lessons that were derived
from this rich legacy included the following:

@@

We have developed, tested and deployed the Teleo-Reactive EXecutive
(\rxe) an on-board adaptive control system that integrates AI based
planning and state estimation in a hybrid
executive\cite{mcgann08a,mcgann08b,py10}.  State estimation allows the
system to keep track of world evolution as time advances based on a
formal model distributed through the architecture.  Onboard planning
and execution enables adaptation of navigation and instrument control
based on the state identified during state estimation.  It further
enables goal-directed commanding within the context of projected
mission state and allows for replanning for off-nominal situations and
opportunistic science events. The framework in addition to being used
on an AUV, is general enough \kcomment{to} be used for controlling a
personal robot \cite{pr2,Meeussen:2010dn,mcgann2009} and is deployed
on a European planetary rover testbed \cite{goac11}. While it is
possible to integrate probabilistic estimation on top of this
framework \cite{mcgann08d}, such representation is not explicitly
handled by the framework and is out of scope of this chapter.
Deliberation and reaction are integrated systematically over different
temporal and functional scopes within a single agent and a single
model that covers the needs of high-level mission management,
low-level navigation, instrument control, and detection of
unstructured and poorly understood phenomena. \rx is deployed on
MBARI's \emph{Dorado} AUV shown in Fig. \ref{fig:auv-fig}, which to
the best of our knowledge is the only operational marine platform
anywhere being used for routine scientific surveys with onboard plan
synthesis.

@@

This chapter is organized as follows. We start with some foundational
concepts in our Planning framework in Section~\ref{sec:concepts} which
includes a brief overview of AI Planning in
Section~\ref{sec:planningfound}. In Section~\ref{sec:basics} we go
deeper into the \eu framework itself, the basis of all deliberation
within \rxe. A key portion is Section~\ref{sec:europa:pr} which
details the internal plan representation within a situated agent like
\rxe. Modeling (Section~\ref{sec:europa:modeling}), Inference
(Section~\ref{sec:europa:inference}) and Search
(Section~\ref{sec:europa:search}) articulates important details
associated with \eu critical to \rxe.  With these foundational
elements of deliberation out of the way, we transition to \rx itself
in Section~\ref{sec:arch}, bring out architectural details in
Section~\ref{sec:arch:trex}, deal with the execution cycle in
Section~\ref{sec:arch:exec}, highlight how \rx deliberates in
Section~\ref{sec:arch:europa}, finally delving deeper into the key
concept of synchronization in Section~\ref{sec:arch:synch}. Further
details on deliberation within \rx (Section~\ref{sec:arch:plan}) and
how planning and execution are interleaved are shown in
Section~\ref{sec:arch:intertwine}. We offer results from our
experiments at sea in Section~\ref{sec:results}, offer some insights
into the near-term future goals of our research in
Section~\ref{sec:future} and conclude with
Section~\ref{sec:conclusion}.
